\documentclass[oneside, 12pt, a4paper]{book}

\errorcontextlines=5 % Adjust the number to show more or fewer lines

\makeatletter
\def\input@path{{./templates/}}
\usepackage{thesis_uc3m}
\usepackage{eurosym}
\usepackage{longtable}
\graphicspath{{./figures} {./templates/figures}}
\makeatother

\title{Building a Scalable Parking Management Solution for Multi-Community Deployment}
\author{Andrés Navarro Pedregal}
\degree{Data Science and Engineering and Telecommunication Technologies Engineering}
\graduationyear{2024~--~2025}
\supervisor{David Larrabeiti López}
\placeandyear{Leganés, 2025 \\ Madrid, Spain}

\hypersetup{
  pdfauthor=Andres Navarro Pedregal,
  pdftitle=Final Thesis | Andres Navarro Pedregal | Telecommunication Technologies Engineering,
  pdfsubject=Final Thesis,
  pdfkeywords={Final Thesis, Andres Navarro Pedregal, Telecommunication Technologies Engineering},
}

\addbibresource{./bibliography.bib} % load the bibliography file

\loadglsentries{acronyms} % load the acronyms file

\begin{document}

% \setcounter{tocdepth}{0} % Show only parts and chapters in the table of contents

\frontmatter
\maketitle

\blankpage%
\chapter*{Abstract}

This bachelor thesis presents the design, implementation, and deployment of a distributed parking management system tailored for multi-community environments. The project addresses the growing challenges of urban parking management through an innovative approach that combines edge computing with cloud services.

The system employs a distributed architecture where each community operates autonomously while maintaining centralized oversight. Key components include license plate recognition using machine learning, automated access control, and a web-based management interface. The solution utilizes NVIDIA Jetson Nano devices for edge processing, custom relay boards for hardware control, and AWS cloud infrastructure for centralized management.

The system has been successfully deployed across ten communities in Valencia, Spain, demonstrating its scalability and reliability in real-world conditions. The implementation incorporates robust security measures, including encrypted databases, secure network communications via ZeroTier, and SMS-based user authentication. Environmental challenges, such as the Dana weather event in September 2024, led to system improvements in hardware protection and reliability.

This work contributes to the field of smart city infrastructure by providing a practical, scalable solution for community parking management that balances autonomy with centralized control, setting a foundation for future expansion and enhancement of urban parking solutions.

\textbf{Keywords:} parking management, distributed systems, edge computing, cloud computing, license plate recognition, IoT, smart cities

\blankpage%

\chapter*{Acknowledgments}
\begingroup
\let\clearpage\relax % This temporarily disables \clearpage so the Agradecimientos chapter is on the same page

First and foremost, I would like to express my sincere gratitude to my supervisor, Dr. David Larrabeiti López, for the opportunity to work with him on this project. His guidance, expertise, and support have been invaluable throughout the development of this thesis.

My heartfelt appreciation goes to the Telematics Department of Universidad Carlos III de Madrid, especially to my supervisor again and Dr. José Alberto Hernández Gutiérrez for their unwavering support since the beginning of my academic journey. I am grateful to all members of the department for creating a nurturing and stimulating environment for research and learning.

To ATES, specially Jose Peris for their support and collaboration in the development of the parking management system.

Finally, I would like to thank my colleague Álvaro Ramajo for his collaboration and support throughout this process. Your camaraderie and intellectual contributions have been instrumental in the completion of this thesis.

To all those mentioned and to the many others who have supported me along the way, thank you for your encouragement, patience, and belief in my abilities. This work would not have been possible without you.

\chapter*{Agradecimientos}

En primer lugar, quiero expresar mi más sincero agradecimiento a mi supervisor, el David Larrabeiti López, por la oportunidad de trabajar con él en este proyecto. Su orientación, experiencia y apoyo han sido invaluables durante todo el desarrollo de esta tesis.

Mi más profundo aprecio va para el Departamento de Telemática de la Universidad Carlos III de Madrid, especialmente otra vez a mi supervisor y Dr. José Alberto Hernández Gutiérrez por el apoyo inquebrantable desde el inicio de mi trayectoria académica. Estoy agradecido a todos los miembros del departamento por crear un ambiente estimulante y enriquecedor para la investigación y el aprendizaje.

A ATES, especialmente a Jose Peris por su apoyo y colaboración en el desarrollo de este sistema.

Finalmente, me gustaría agradecer a mi colega Álvaro Ramajo por su colaboración y apoyo durante todo este proceso. Tu camaradería y contribuciones intelectuales han sido fundamentales para la realización de esta tesis.

A todos los mencionados y a los muchos otros que me han apoyado en el camino, gracias por su aliento, paciencia y fe en mis capacidades. Este trabajo no habría sido posible sin ustedes.

\endgroup

\blankpage%

\renewcommand{\contentsname}{Table of Contents}
\tableofcontents

\blankpage%

\listoffigures

\blankpage%

\listoftables

\blankpage%

\printglossary[type=\acronymtype,style=long, title=LIST OF ACROYNMS]

\blankpage%

\mainmatter%

\oldpart{Introduction} % This is the first part, so it is not preceded by a new page

\input{src/motivation}
\input{src/statement_of_problem}
\input{src/objectives}
\input{src/document_structure}
\input{src/methodology_approach}

\oldpart{Theoretical Background}\label{part:theoretical_background}

\input{src/cloud_computing}
\input{src/iot}

\oldpart{State of the art}\label{part:state_of_the_art}

\input{src/historical_development}
\input{src/modern_trends}

\oldpart{Methodology}\label{part:methodology}

\input{src/requirements}
\input{src/design}
\input{src/implementation}

\oldpart{Results}\label{part:results}

\input{src/testing}
\input{src/deployment}

\oldpart{Conclusions}\label{part:conclusions}

\input{src/conclusions}
\input{src/future_work}
\input{src/socio_economic_environment}
\input{src/regulatory_framework}

\blankpage%
\printbibliography%

\end{document}
