
\chapter{Objectives}\label{ch:objectives}

The primary goal of this bachelor thesis is to design and implement a distributed parking management system to address the evolving needs of smart cities. The project aims to overcome the limitations of existing parking management solutions by utilizing scalable and \gls{IoT} technologies. By doing so, it seeks to enhance performance, security, and user experience, contributing to the development of smart city solutions. The specific objectives of the project are outlined below:

\begin{itemize}
	\item \textbf{Analyze Existing Systems:} Review current parking management systems, identifying inefficiencies and challenges. This includes assessing the limitations of centralized systems and understanding the needs of users (drivers and facility managers) to uncover areas for improvement using a distributed approach.

	\item \textbf{Evaluate Relevant Technologies:} Examine key technologies used in parking management systems, focusing on their suitability for a distributed architecture. This involves evaluating \gls{iot} devices, sensors, communication protocols, and data storage methods to determine the most scalable and secure technologies for the proposed system.

	\item \textbf{Design the System Architecture:} Develop the overall design of the distributed parking management system. This includes selecting \gls{iot} sensors, determining data storage solutions, and ensuring that the system can handle high data loads while integrating seamlessly with other smart city systems.

	\item \textbf{System Development:} Implement the system using an agile approach, following best practices in software engineering. This includes iterative planning, design, coding, testing, deployment, and maintenance, with an emphasis on modularity and extensibility to accommodate future updates and integration with emerging technologies (e.g., autonomous vehicles, AI-based traffic management).

	\item \textbf{Evaluate System Performance:} Assess the implemented system's performance based on \glspl{kpi} such as scalability, reliability, data accuracy, and real-time processing capabilities to ensure the system meets its design objectives.

	\item \textbf{Real-World Testing and Validation:} Deploy the system in a real-world urban environment with limited parking capacity. The goal is to validate the system’s effectiveness in managing parking allocation, optimizing resource use, and reducing congestion while testing its robustness, scalability, and performance under actual conditions.

\end{itemize}

