\chapter{Statement of the problem}\label{ch:statement_of_problem}

The lack of efficient \glspl{pms} is a pervasive problem in modern cities, exacerbated by the growing number of vehicles and the resulting increase in urban population. Traditional manual \glspl{pms} have proven inadequate in addressing the complexities of modern urban parking, leading to higher costs, longer search times, traffic congestion, and elevated levels of urban pollution. The ongoing development of \glspl{pms} remains a crucial research area, as citizens favor systems that prioritize user-friendliness, security, and reliability \autocite{parking_choices} \autocite{A_Elsonbaty_2020} \autocite{intelligent_parking_system} \autocite{smart_parking_management_system}.

This project aims to address the gap by designing and implementing a fully distributed \gls{pms} tailored for the next generation of smart cities. The proposed system will focus on addressing the inefficiencies and challenges inherent in current \glspl{pms} through a distributed approach that leverages modern technologies.

Given the broad nature of this problem, the scope of this project will be narrowed to a specific environment and use case, as outlined below:

\begin{itemize}
    \item \textbf{Environment:} The system will be designed for urban environments with high vehicle density and limited parking spaces. The case study will focus on a city center with a high volume of vehicles and limited parking availability, reflecting the challenges faced by many modern cities.

    \item \textbf{Atmospheric Conditions:} The system will be designed to operate under typical urban atmospheric conditions, with no specific constraints on temperature, pressure, or humidity. The system will be designed to function in a variety of weather conditions, including rain, heat, and cold.

    \item \textbf{Operational Parameters:} The system will be designed to manage parking spaces in a city center, with a focus on optimizing space utilization, reducing search times, and minimizing traffic congestion. The system will be scalable to accommodate a large number of parking spaces and users.

    \item \textbf{Hardware:} The system will be designed to leverage modern technologies such as \gls{iot} devices, sensors, and cloud computing to provide real-time monitoring and management of parking spaces. The system will be designed to be cost-effective, scalable, and user-friendly.
\end{itemize}
