\chapter{Testing}\label{ch:testing}

The testing phase of this parking management system follows a comprehensive approach as outlined in \cref{ch:methodology_approach}, beginning with individual component testing before progressing to integrated system validation. This methodical approach ensures that each component functions correctly in isolation before examining their interaction within the complete system.

\todo{add images}

\section{Individual Tests}

The database testing phase focused on ensuring data integrity and proper relationship management through rigorous SQL query testing. Multiple database iterations were conducted to refine data categories and verify correct data representation. Critical tests included validating constraints such as boolean attributes being limited to 0 and 1 values, and ensuring logical consistency in numerical fields like preventing negative values for parking space allocations. This thorough validation process helped establish a robust foundation for data storage and manipulation.

The terminal testing concentrated on validating the API endpoints using Insomnia \autocite{insomnia2025}, a specialized tool for API testing and documentation. Each endpoint underwent systematic testing to verify correct functionality, proper error handling, and expected response formats. This process generated comprehensive documentation of API behaviors and interactions, creating a valuable reference for future development and maintenance.

Server testing incorporated both visual interface validation and functional integration testing. The visual testing focused on ensuring proper website rendering across different devices and screen sizes using the Responsive Design Mode available in Firefox and Google Chrome's developer tools. Additionally, extensive integration testing was performed to verify seamless communication between the server and terminal components in a local environment.

\section{Controlled Environment Tests}

System-wide testing was conducted in actual parking facilities to validate real-world performance. These tests revealed several important considerations regarding network connectivity. Various cellular network providers were evaluated to identify the most reliable connection for different deployment locations. Network resilience testing included scenarios with poor connection quality and complete connection loss to ensure system stability.

\todo{add the infrared part for problems}

\todo{add rele problems}

The testing phase highlighted several areas requiring additional attention, particularly regarding network reliability and hardware interactions. These findings led to important system refinements and the development of robust fallback mechanisms to maintain system functionality under suboptimal conditions.

